---
title: "Day 8 Homework"
output: html_document
---
```{r}
library(dplyr)
library(reshape2)
CUdata <- read.csv("C:/Users/Alison/Desktop/Jan R Course/CUdata.csv")
```
```{r}
CUdata$Group <- "6U"
CUdata$Group[CUdata$Age == "6" & CUdata$Condition == "Non-Unitized"] <- "6NU"
CUdata$Group[CUdata$Age == "8" & CUdata$Condition == "Non-Unitized"] <- "8NU"
CUdata$Group[CUdata$Age == "8" & CUdata$Condition == "Unitized"] <- "8U"
CUdata$Group <- as.factor(CUdata$Group)
levels(CUdata$Group)

cudata <- CUdata[!is.na(CUdata$Source.Correct), ]
```


1. Try to recreate the results of Homework 6 (or your intended results) using the `dplyr` functions.
```{r}
#find mean for each group
cudata %>%
  group_by(Group) %>%
  summarize(mean= mean(Source.Correct))
```



2. Find another kind of analysis/transformation/summary stat that you want to apply across multiple groups in your data. Use the functions from `reshape2` and `dplyr` to get these results.

```{r}
#means only for participants who took at least 15 mins at retrieval
cudata$RetrievalTime <- as.numeric(cudata$RetrievalTime)

cudata %>%
  filter(RetrievalTime > 15) %>%
   group_by(Group) %>%
  summarize(mean= mean(Source.Correct))

#try only when Encoding Time between 30 & 45 mins

cudata$EncodingTime <- as.numeric(cudata$EncodingTime)

cudata %>%
  filter(EncodingTime >30) %>%
  filter(EncodingTime <45) %>%
   group_by(Group) %>%
  summarize(mean= mean(Source.Correct))


```

3. For more practice, try another example of something like #2 (find another stat or grouping or something).

```{r}
#see if groups differed between set A and set B
cudata$Set <- as.factor(cudata$Set)

cudata %>%
  group_by(Group , Set) %>%
  summarize(mean= mean(Source.Correct))
```

4. Do yet another case of #2 above, but this time throw in a transformation, too.

```{r}
cudata %>%
  group_by(Group) %>%
  summarize(mean= mean(log(Source.Correct)))
```