---
title: "Day 3 Homework"
output: html_document
---
```{r}
library(reshape2)
CUdata <- read.csv("C:/Users/arobey/Dropbox/Jan R Course/CUdata.csv")
```

The goal of this homework is to get practice with manipulating data.

1. Make both a "wide" and a "long" version of your data

Long Version
```{r}
CUdata.melt1 <- melt(CUdata, measure.vars = c("TrainingTime", "EncodingTime", "BreakTime", "RetrievalTime", "TotalTime"), variable.name = "StudySection", value.name = "minutes")

CUdata.melt2 <- melt(CUdata.melt1, measure.vars = c("N.6", "N.5", "N.4", "N.3", "N.2", "N.1", "Y.6", "Y.5", "Y.4", "Y.3", "Y.2", "Y.1", "R.6", "R.5", "R.4", "R.3", "R.2", "R.1"), variable.name = "ConfidenceRating", value.name = "NConfidenceRating")

#Can the above all be done in 1 step?
```

My original data is in Wide version, but can also use dcast to get it back
```{r}


CUdata.cast1 <- dcast(CUdata.melt2, ID+Initials+Condition+SessionDate+Time+Tester+Set+FullTerm+Birthday+Age+ExactAge+Ethnicity+Race+CorrectTraining+Notes+Hits+Misses+Accuracy+Recollection+Familiarity+SSE+Convergence+LinearFiT+PolyFit+X2term +ConfidenceRating+NConfidenceRating ~ StudySection, value.var = "minutes" )

#Is there a way to not have to write out every Colname on the left side of the formula? I tried several version of this:
#DoCast<-colnames(CUdata.melt2)
#DontCast <- c("StudySection", "minutes")

#DoCast2<-DoCast[!DoCast %in% DontCast]
#but couldn't get it to work

CUdata.cast2 <- dcast(CUdata.cast1, ID+Initials+Condition+SessionDate+Time+Tester+Set+FullTerm+Birthday+Age+ExactAge+Ethnicity+Race+CorrectTraining+Notes+Hits+Misses+Accuracy+Recollection+Familiarity+SSE+Convergence+LinearFiT+PolyFit+X2term + TrainingTime + EncodingTime + BreakTime + RetrievalTime + TotalTime ~ ConfidenceRating, value.var = "NConfidenceRating" )

```


2. Transform a variable
```{r}
CUdata$HitProportion <- CUdata$Hit/120
```

3. Recode a factor
```{r}
CUdata$Age<- as.factor(CUdata$Age)
summary(CUdata$Age)
levels(CUdata$Age)
levels(CUdata$Age) <- c("6yo", "8yo")

#Trying to avoid usings numbers as labels for my factor so changed to 6yo and 8yo
```

4. Add a new factor, where the levels are conditional on the values of some other variable. E.g., a factor of "high", "medium", and "low" based on thresholds for another variable.

```{r}
CUdata$EncodingTime <- as.numeric(CUdata$EncodingTime)
summary(CUdata$EncodingTime)
CUdata$speed<- "medium"
CUdata$speed[CUdata$EncodingTime < 14.75]<- "fast"
CUdata$speed[CUdata$EncodingTime > 42] <- "slow"
CUdata$speed<- as.factor(CUdata$speed)
summary(CUdata$speed)
```

5. Reorder the levels of this new factor
```{r}
levels(CUdata$speed)
CUdata$speed <- factor(CUdata$speed, levels = c("slow", "medium", "fast"))
levels(CUdata$speed)
```

6. Choose a factor that could be re-coded as multiple dimensions (recall the sepal/petal vs. length/width breakdown). If you don't have one, try to create one.  Now create two (or more) new factors that represent these dimensions.

#for CUdata.melt2 I will separate the confidence Ratings between color and number
```{r}
CUdata.melt3 <- cbind(CUdata.melt2, 
                      colsplit(CUdata.melt2$ConfidenceRating, pattern = "\\.", 
                               names = c("color", "ConfidenceLevel")))

```

7. Using `dcast`, aggregate some variable into "cell means" of some kind.

```{r}

CUdata.cast4 <- dcast(CUdata.melt3, ID+Initials+Condition+SessionDate+Time+Tester+Set+FullTerm+Birthday+Age+Ethnicity+CorrectTraining+Notes+Hits+Misses+Accuracy+Recollection+Familiarity+SSE+Convergence+LinearFiT+PolyFit+X2term + StudySection+minutes +ConfidenceRating +ConfidenceLevel + NConfidenceRating +color ~ Race, value.var = "ExactAge", fun.aggregate = mean )

#not very practical, but I could get it to run (the Race varialbe is a mess and not something I actually plan on using). I tried doing below but kept getting errors 

CUdata.cast4 <- dcast(CUdata.melt3, ID+Initials+Condition+SessionDate+Time+Tester+Set+FullTerm+Birthday+Age+ExactAge+Ethnicity+Race+CorrectTraining+Notes+Hits+Misses+Accuracy+Recollection+Familiarity+SSE+Convergence+LinearFiT+PolyFit+X2term + StudySection+minutes +ConfidenceRating +ConfidenceLevel  ~ color, value.var = "NConfidenceRating", fun.aggregate = mean, na.rm=TRUE )

#I thought for each subject this would take the average NConfidenceRating across the 6 levels for each color (N, Y, R) so for N it would average N1,N2,N3,N4, N5 & N6...suggestions?

```

8.  Save all of the above in a well-documented R Markdown document.  Email me the .Rmd file (and if you use different or updated data from Day 2 Homework, send that to me, too).
