---
title: "Day 4 Homework"
output: html_document
---
```{r}
CUdata <- read.csv("C:/Users/arobey/Dropbox/Jan R Course/CUdata.csv")
```

1. Change the column names of your data to something easier to work with.  If you like your column names, change them into something else reasonable, just for practice.

```{r}
oldnames <- colnames(CUdata)
mycolnames <- c("ID", "Initials","Condition", "Date","Time", "Experimenter", "StimulusSet", "Fullterm", "Birthday", "AgeGroup", "ExactAge", "Ethnicity", "Race", "Training", "Encoding", "Break" , "Retrieval", "TotalTime", "Training Correct" , "SessionNotes", "SourceCorrect", "SourceIncorrect", "Accuracy", "n6", "n5", "n4", "n3", "n2", "n1", "y6", "y5", "y4", "y3", "y2", "y1", "r6", "r5", "r4", "r3", "r2", "r1", "recollection", "familiarity", "SSE", "Convergence", "LinFit", "PolyFit", "X2")
colnames(CUdata) <- mycolnames
data.frame(oldnames,mycolnames)

```
2. List ALL the issues you can see where it looks like your data is being read in a weird way.  If your data looks perfect, find some way to mess it up :-)

#The Convergence column should all be NA because that variables hasn't been calculated yet (it should be the same as recollection, familiarity, and SSE)

#There are several variables in the FullTerm column that should be NAs (currently they are ???, blank, or need to ask)

#Same is true in ethnicity, race, some of the Time variables 


3. Pick one or two of the most egregious or problematic of the issues in #2 and fix them.

```{r}
summary(CUdata$Convergence)
CUdata$Convergence<- rep(NA)

CUdata$Fullterm[c(4,17,22,24,37,41,44,45,50,59)] <- NA
```

###Example of how to combine coulmns if data only in 1 of the 2
```{r}
mydata <- data.frame(ColA = c(NA,1,2,NA, NA), ColB = c(45, NA, NA, 2, 99))

mydata$ColC<- mydata$ColA
mydata$ColC[is.na(mydata$ColC)]

mydata$ColC[is.na(mydata$ColC)] <- mydata$ColB[is.na(mydata$ColA)]
mydata
```



4. Check for NAs, and report where you see them (try to pinpoint where they are, not just "5 NAs in column seven".
```{r}
summary(CUdata)
#View(CUdata)
#View(CUdata[ , c(1, 21,22,23,24)])
#out  for the sake of knitting
```
### CAn also do:
which(is.na(mydata[ ,1]))
#will tell you which rows in a particular column are NAs

###Can also use 
```{r}
?complete.cases
complete.cases(mydata)
mydata[complete.cases(mydata), ]
mydata[complete.cases(mydata), ]
```

#Fullterm columns rows 4,17,22,24,37,41,44,45,50 & 59
#SourceCorrect, SourceIncorrect, & Accuray (and the Confidence) in rows 15,16,17,18,34,35,36,37,45,46,47,57,58,59,60
#All of the recollection, familiarity, SSE, and convergence columns 

5. Decide what you think you should do about the NAs, and say why.  If you can, try to implement this decision.
#Fullterm columns rows 4,17,22,24,37,41,44,45,50 & 59
  #not a problem not using this variable
#SourceCorrect, SourceIncorrect, & Accuray (and the Confidence) in rows 15,16,17,18,34,35,36,37,45,46,47,57,58,59,60
  #should get rid of these
#All of the recollection, familiarity, SSE, and convergence columns 
  #not a problem, not calculated yet
  
```{r}
CUdataClean <- CUdata[!is.na(CUdata$SourceCorrect), ]

```

6. Remove any problematic rows and/or columns.  Say why you want to remove them.  If there aren't any problems, describe why you think there are no problems.

#see number 5

7. Re-code at least one factor.  Provide a table that shows the correspondence between old levels and new levels.
```{r}
CUdata$AgeGroup <- as.factor(CUdata$AgeGroup)
oldlevels<- levels(CUdata$AgeGroup)
levels(CUdata$AgeGroup) <- c("6yo", "8yo")
data.frame(oldlevels, levels(CUdata$AgeGroup))
```

8. Run TWO DIFFERENT simple analyses or statistical tests, such as linear regression (`lm()`), logistic regression (`glm()`), correlation test (`cor.test()`), t-test (`t.test()`), or non-parametric tests (e.g., `wilcox.test()`).  For each of these:
  - Describe why you are doing this analysis, i.e., what question is it answering?
  - I won't judge you on statistical expertise!  (though I will make comments if I think I can be helpful)
  - Report some key statistics from the analysis, using inline code
  
```{r}
AgeDiff<-t.test(Accuracy ~ AgeGroup, data = CUdataClean)
AgeDiff
names(AgeDiff)
AgeDiff$"p.value"
```
This was a test to see if there was a different in accuracy between age groups, becuase p = `r AgeDiff$"p.value" ` there is no significant difference.  

```{r}
CUdataClean$Encoding<- as.numeric(CUdataClean$Encoding)
CUdataClean$Accuracy<- as.numeric(CUdataClean$Accuracy)

EncodingAccuracy<-cor.test (CUdataClean$Encoding, CUdataClean$Accuracy, method = "pearson")
names(EncodingAccuracy)
EncodingAccuracy$estimate
```
This was a test to see the correlation between amount of time spent at encoding and accuracy at retrieval, the test found r = `r EncodingAccuracy$estimate ` .

can add round(value, #of decimal places) to round the inline code 
  
  